\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-12-30 forwards-and-backwards.tex
submitted!

Now, taking expectations in~(\ref{eqn:eta_f_mgale_decomp}),
    \begin{align}
\label{bound on intfdeta}
        \IE\left[ \langle f, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle f, \eta^N_0 \rangle \right]
        + C_f \int_0^t \IE\left[ \langle 1 + |f|, \eta^N_s \rangle \right] dt .
    \end{align}
The bound~(\ref{eta_f_bound}) then follows by first applying Gronwall's
inequality in the case $f=1$, which yields
\[
	\IE\big[\langle 1,\eta_t^N\rangle\big]\leq e^{Ct}\IE\big[\langle 1,\eta_0^N\rangle\big],
\]
with $C$ independent of $N$, and then using that $|f|$ is bounded and
substituting the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
expression above.
\end{proof}

>>>>

Now, taking expectations in~(\ref{eqn:eta_f_mgale_decomp}),
    \begin{align}
\label{bound on intfdeta}
        \IE\left[ \langle f, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle f, \eta^N_0 \rangle \right]
        + C_f \int_0^t \IE\left[ \langle 1 + |f|, \eta^N_s \rangle \right] dt .
    \end{align}
The bound~(\ref{eta_f_bound}) then follows by first applying Gronwall's
inequality in the case $f=1$, which yields
\[
	\IE\big[\langle 1,\eta_t^N\rangle\big]\leq e^{Ct}\IE\big[\langle 1,\eta_0^N\rangle\big],
\]
with $C$ independent of $N$, and
substituting the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
expression above.
\end{proof}
